---
title: "CorShrink on *huge* graphs - Band network"
author: "Kushal K Dey"
date: "1/1/2018"
output: html_document
---

This is one in a bunch of simulation examples of data possessing different graphical structures. we use the package **huge** to generate the different examples and then run GLASSO under various regularization parameter choices.

```{r setup, include=FALSE}
library(CorShrink)
library(huge)
library(corpcor)
```


## n=10, d = 200

### Simulation

```{r}
library(huge) # Load the package huge
L = huge.generator(n=10,d=200,graph="band", g=5) # Generate data with band structures
X = L$data; 
```

```{r}
col=c(rep(rgb(0,1,0), 10000),rev(rgb(seq(1,0,length=1000),1,seq(1,0,length=1000))),
      rgb(1,seq(1,0,length=1000),seq(1,0,length=1000)), rep(rgb(1,0,0),10000))

image(as.matrix(cov2cor(L$sigma)),
      col=col, main=paste0("pop corr matrix"), cex.main=1,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))
```

### Covariance estimation

```{r}
##  GLASSO

out.gl = huge(X, lambda = seq(0.98, 0.01, length.out = 100), method = "glasso", cov.output = TRUE)
out.npn = huge.select(out.gl)

est_icov <- out.npn$opt.icov
est_cov <- out.npn$opt.icov

## Shafer Strimmer 

strimmer_sample <- corpcor::cor.shrink(out.npn$data)

## CorShrink

cov_sample_ML <-  CorShrinkData(out.npn$data, sd_boot = FALSE, optmethod = "mixEM",
                     image.control = list(x.cex = 0.3, y.cex = 0.3),
                     ash.control = list())

```

### Visualization

GLASSO inverse correlation matrix.

```{r}
image(cov2cor(as.matrix(est_icov)),
      col=col, main=paste0("GLASSO"), cex.main=1,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

```

All methods - covariance matrix 

```{r}

col=c(rep(rgb(0,1,0), 10000),rev(rgb(seq(1,0,length=1000),1,seq(1,0,length=1000))),
      rgb(1,seq(1,0,length=1000),seq(1,0,length=1000)), rep(rgb(1,0,0),10000))

par(mfrow = c(2,2))

image(as.matrix(cor(out.npn$data)),
      col=col, main=paste0("sample corr matrix"), cex.main=1,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

image(cov2cor(as.matrix(est_cov)),
      col=col, main=paste0("GLASSO"), cex.main=1,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

image(strimmer_sample,
      col=col, main=paste0("shafer strimmer"), cex.main=2,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

image(as.matrix(cov_sample_ML$ash_cor_PD),
      col=col, main=paste0("CorShrink"), cex.main=2,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

```



## n=50, d = 200

### Simulation

```{r}
library(huge) # Load the package huge
L = huge.generator(n=50,d=200,graph="band", g=5) # Generate data with band structures
X = L$data; 
```

```{r}
col=c(rep(rgb(0,1,0), 10000),rev(rgb(seq(1,0,length=1000),1,seq(1,0,length=1000))),
      rgb(1,seq(1,0,length=1000),seq(1,0,length=1000)), rep(rgb(1,0,0),10000))

image(as.matrix(cov2cor(L$sigma)),
      col=col, main=paste0("pop corr matrix"), cex.main=1,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))
```

### Covariance estimation

```{r}
##  GLASSO

out.gl = huge(X, lambda = seq(0.98, 0.01, length.out = 100), method = "glasso", cov.output = TRUE)
out.npn = huge.select(out.gl)

est_icov <- out.npn$opt.icov
est_cov <- out.npn$opt.icov

## Shafer Strimmer 

strimmer_sample <- corpcor::cor.shrink(out.npn$data)

## CorShrink

cov_sample_ML <-  CorShrinkData(out.npn$data, sd_boot = FALSE, optmethod = "mixEM",
                     image.control = list(x.cex = 0.3, y.cex = 0.3))

```

### Visualization

GLASSO inverse correlation matrix.

```{r}
image(cov2cor(as.matrix(est_icov)),
      col=col, main=paste0("GLASSO"), cex.main=1,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

```

All methods - covariance matrix 

```{r}

col=c(rep(rgb(0,1,0), 10000),rev(rgb(seq(1,0,length=1000),1,seq(1,0,length=1000))),
      rgb(1,seq(1,0,length=1000),seq(1,0,length=1000)), rep(rgb(1,0,0),10000))

par(mfrow = c(2,2))

image(as.matrix(cor(out.npn$data)),
      col=col, main=paste0("sample corr matrix"), cex.main=1,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

image(cov2cor(as.matrix(est_cov)),
      col=col, main=paste0("GLASSO"), cex.main=1,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

image(strimmer_sample,
      col=col, main=paste0("shafer strimmer"), cex.main=2,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

image(as.matrix(cov_sample_ML$ash_cor_PD),
      col=col, main=paste0("CorShrink"), cex.main=2,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

```


## n=100, d = 200

### Simulation

```{r}
library(huge) # Load the package huge
L = huge.generator(n=50,d=200,graph="band", g=5) # Generate data with band structures
X = L$data; 
```

```{r}
col=c(rep(rgb(0,1,0), 10000),rev(rgb(seq(1,0,length=1000),1,seq(1,0,length=1000))),
      rgb(1,seq(1,0,length=1000),seq(1,0,length=1000)), rep(rgb(1,0,0),10000))

image(as.matrix(cov2cor(L$sigma)),
      col=col, main=paste0("pop corr matrix"), cex.main=1,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))
```

### Covariance estimation

```{r}
##  GLASSO

out.gl = huge(X, lambda = seq(0.98, 0.01, length.out = 100), method = "glasso", cov.output = TRUE)
out.npn = huge.select(out.gl)

est_icov <- out.npn$opt.icov
est_cov <- out.npn$opt.icov

## Shafer Strimmer 

strimmer_sample <- corpcor::cor.shrink(out.npn$data)

## CorShrink

cov_sample_ML <-  CorShrinkData(out.npn$data, sd_boot = FALSE, optmethod = "mixEM",
                     image.control = list(x.cex = 0.3, y.cex = 0.3))

```

### Visualization

GLASSO inverse correlation matrix.

```{r}
image(cov2cor(as.matrix(est_icov)),
      col=col, main=paste0("GLASSO"), cex.main=1,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

```

All methods - covariance matrix 

```{r}

col=c(rep(rgb(0,1,0), 10000),rev(rgb(seq(1,0,length=1000),1,seq(1,0,length=1000))),
      rgb(1,seq(1,0,length=1000),seq(1,0,length=1000)), rep(rgb(1,0,0),10000))

par(mfrow = c(2,2))

image(as.matrix(cor(out.npn$data)),
      col=col, main=paste0("sample corr matrix"), cex.main=1,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

image(cov2cor(as.matrix(est_cov)),
      col=col, main=paste0("GLASSO"), cex.main=1,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

image(strimmer_sample,
      col=col, main=paste0("shafer strimmer"), cex.main=2,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

image(as.matrix(cov_sample_ML$ash_cor_PD),
      col=col, main=paste0("CorShrink"), cex.main=2,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

```


## n=200, d = 200

### Simulation

```{r}
library(huge) # Load the package huge
L = huge.generator(n=50,d=200,graph="band", g=5) # Generate data with band structures
X = L$data; 
```

```{r}
col=c(rep(rgb(0,1,0), 10000),rev(rgb(seq(1,0,length=1000),1,seq(1,0,length=1000))),
      rgb(1,seq(1,0,length=1000),seq(1,0,length=1000)), rep(rgb(1,0,0),10000))

image(as.matrix(cov2cor(L$sigma)),
      col=col, main=paste0("pop corr matrix"), cex.main=1,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))
```

### Covariance estimation

```{r}
##  GLASSO

out.gl = huge(X, lambda = seq(0.98, 0.01, length.out = 100), method = "glasso", cov.output = TRUE)
out.npn = huge.select(out.gl)

est_icov <- out.npn$opt.icov
est_cov <- out.npn$opt.icov

## Shafer Strimmer 

strimmer_sample <- corpcor::cor.shrink(out.npn$data)

## CorShrink

cov_sample_ML <-  CorShrinkData(out.npn$data, sd_boot = FALSE, optmethod = "mixEM",
                     image.control = list(x.cex = 0.3, y.cex = 0.3))

```

### Visualization

GLASSO inverse correlation matrix.

```{r}
image(cov2cor(as.matrix(est_icov)),
      col=col, main=paste0("GLASSO"), cex.main=1,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

```

All methods - covariance matrix 

```{r}

col=c(rep(rgb(0,1,0), 10000),rev(rgb(seq(1,0,length=1000),1,seq(1,0,length=1000))),
      rgb(1,seq(1,0,length=1000),seq(1,0,length=1000)), rep(rgb(1,0,0),10000))

par(mfrow = c(2,2))

image(as.matrix(cor(out.npn$data)),
      col=col, main=paste0("sample corr matrix"), cex.main=1,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

image(cov2cor(as.matrix(est_cov)),
      col=col, main=paste0("GLASSO"), cex.main=1,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

image(strimmer_sample,
      col=col, main=paste0("shafer strimmer"), cex.main=2,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

image(as.matrix(cov_sample_ML$ash_cor_PD),
      col=col, main=paste0("CorShrink"), cex.main=2,
      xaxt = "n", yaxt = "n", zlim=c(-1,1))

```



