---
title: "sqrt eigenvalues trend plots"
author: "Kushal K Dey"
date: "3/31/2018"
output: html_document
---

Here we plot the trends of the square root of the eigenvalues of the estimated correlation
matrices using different approaches - CorShrink, glasso and corpcor - against the tru
correlation matrix. 

```{r}
library(ggplot2)
library(gridExtra)
```


## Simulation Scripts

We run the following scripts for different choices of $n$ and $p$ for the Hub, Toeplitz and 
Banded Precision matrices.

### Hub

```{r echo=TRUE, eval=FALSE}
source("../code/Figure2/eigenvalues_distribution_hub.R")
```

### Toeplitz

```{r echo=TRUE, eval=FALSE}
source("../code/Figure2/eigenvalues_distribution_toeplitz.R")
```

### Banded Precision

```{r echo=TRUE, eval=FALSE}
source("../code/Figure2/eigenvalues_distribution_sparse_nonsparse.R")
```

The outputs from running each of these are saved under `/shared_output/eigenvalues_sqrt_distribution/`
and are read as follows to perform the visualization.


## Visualization

```{r}
hub_sqrt_eigenvalues <- get(load("../shared_output/eigenvalues_sqrt_distribution/hub_sqrt_eigenvalues_distribution.rda"))
banded_prec_sqrt_eigenvalues <- get(load("../shared_output/eigenvalues_sqrt_distribution/banded_precision_sqrt_eigenvalues_distribution.rda"))
toeplitz_sqrt_eigenvalues <- get(load("../shared_output/eigenvalues_sqrt_distribution/toeplitz_sqrt_eigenvalues_distribution.rda"))
```

## Example

```{r}
eigenvalue_trends <- hub_sqrt_eigenvalues
num_samp <- c(30, 50, 100, 1000)
num <- 20
eigs.df <- data.frame ("x" = rep(1:num, 9),
                         "y" = eigenvalue_trends[[1]]$mean,
                         "color" = factor(c(rep("empirical", num), 
                                     rep("corpcor",  num), 
                                     rep("corshrink", num), 
                                     rep("pdsce", num),
                                     rep("glasso:1e-02", num),
                                     rep("glasso:0.1", num),
                                     rep("glasso:0.5", num),
                                     rep("glasso:1", num),
                                     rep("true", num)), levels = c("empirical", "corpcor",
                                        "corshrink", "pdsce",
                                        "glasso:1e-02",
                                        "glasso:0.1",
                                        "glasso:0.5",
                                        "glasso:1", "true")),
                         "type" = c(rep("A", 8*num), rep("B", num)))

ggplot(eigs.df, aes(x=x, y=y, colour=color, linetype = color)) + geom_line(lty = 1, lwd = 0.7) +
    scale_linetype_manual(values = c(rep("solid", 4), rep("dashed", 1))) +
    scale_colour_manual(values=c("khaki4", "blue", "green", "gold", "magenta",
                                 "red", "#0072B2", "#CC79A7", "#000000")) + xlab("") + ylab("eigenvalues") +
    theme_bw() 
```


## Plotting Hub sqrt eigenvalues

```{r}
eigenvalue_trends <- hub_sqrt_eigenvalues
num_samp <- c(30, 50, 100, 1000)
num <- 20
gg <- list()
for(i in 1:4){
  eigs.df <- data.frame ("x" = rep(1:num, 9),
                         "y" = eigenvalue_trends[[i]]$mean,
                         "color" = factor(c(rep("empirical", num), 
                                     rep("corpcor",  num), 
                                     rep("corshrink", num), 
                                     rep("pdsce", num),
                                     rep("glasso:1e-02", num),
                                     rep("glasso:0.1", num),
                                     rep("glasso:0.5", num),
                                     rep("glasso:1", num),
                                     rep("true", num)), levels = c("empirical", "corpcor",
                                        "corshrink", "pdsce",
                                        "glasso:1e-02",
                                        "glasso:0.1",
                                        "glasso:0.5",
                                        "glasso:1", "true")),
                         "type" = c(rep("A", 8*num), rep("B", num)))

 gg[[i]] <- ggplot(eigs.df, aes(x=x, y=y, colour=color, linetype = color)) + 
                   geom_line(lty = 1, lwd = 0.7) +
                   scale_linetype_manual(values = c(rep("solid", 4), rep("dashed", 1))) +
                   scale_colour_manual(values=c("khaki4", "blue", "green", "gold", "magenta",
                                 "red", "#0072B2", "#CC79A7", "#000000")) + xlab("") + 
                   ylab("sqrt eigenvalues") + ggtitle(paste0("n = ", num_samp[i], ", p = 100")) + 
                   theme_bw() + theme(legend.position="none")
}

grid.arrange(gg[[1]], gg[[2]], gg[[3]],
             gg[[4]], nrow = 2, ncol = 2)

```


## Plotting Toeplitz sqrt eigenvalues

```{r}
eigenvalue_trends <- toeplitz_sqrt_eigenvalues
num_samp <- c(30, 50, 100, 1000)
num <- 20
for(i in 1:4){
  eigs.df <- data.frame ("x" = rep(1:num, 9),
                         "y" = eigenvalue_trends[[i]]$mean,
                         "color" = factor(c(rep("empirical", num), 
                                     rep("corpcor",  num), 
                                     rep("corshrink", num), 
                                     rep("pdsce", num),
                                     rep("glasso:1e-02", num),
                                     rep("glasso:0.1", num),
                                     rep("glasso:0.5", num),
                                     rep("glasso:1", num),
                                     rep("true", num)), levels = c("empirical", "corpcor",
                                        "corshrink", "pdsce",
                                        "glasso:1e-02",
                                        "glasso:0.1",
                                        "glasso:0.5",
                                        "glasso:1", "true")),
                         "type" = c(rep("A", 8*num), rep("B", num)))

 gg[[(4+i)]] <- ggplot(eigs.df, aes(x=x, y=y, colour=color, linetype = color)) + 
                   geom_line(lty = 1, lwd = 0.7) +
                   scale_linetype_manual(values = c(rep("solid", 4), rep("dashed", 1))) +
                   scale_colour_manual(values=c("khaki4", "blue", "green", "gold", "magenta",
                                 "red", "#0072B2", "#CC79A7", "#000000")) + xlab("") + 
                   ylab("sqrt eigenvalues") + ggtitle(paste0("n = ", num_samp[i], ", p = 100")) + 
                   theme_bw() + theme(legend.position="none")
}

grid.arrange(gg[[5]], gg[[6]], gg[[7]],
             gg[[8]], nrow = 2, ncol = 2)

```


## Plotting banded precision sqrt eigenvalues

```{r}
eigenvalue_trends <- banded_prec_sqrt_eigenvalues
num_samp <- c(30, 50, 100, 1000)
num <- 20
for(i in 1:4){
  eigs.df <- data.frame ("x" = rep(1:num, 9),
                         "y" = eigenvalue_trends[[i]]$mean,
                         "color" = factor(c(rep("empirical", num), 
                                     rep("corpcor",  num), 
                                     rep("corshrink", num), 
                                     rep("pdsce", num),
                                     rep("glasso:1e-02", num),
                                     rep("glasso:0.1", num),
                                     rep("glasso:0.5", num),
                                     rep("glasso:1", num),
                                     rep("true", num)), levels = c("empirical", "corpcor",
                                        "corshrink", "pdsce",
                                        "glasso:1e-02",
                                        "glasso:0.1",
                                        "glasso:0.5",
                                        "glasso:1", "true")),
                         "type" = c(rep("A", 8*num), rep("B", num)))

 gg[[(8+i)]] <- ggplot(eigs.df, aes(x=x, y=y, colour=color, linetype = color)) + 
                   geom_line(lty = 1, lwd = 0.7) +
                   scale_linetype_manual(values = c(rep("solid", 4), rep("dashed", 1))) +
                   scale_colour_manual(values=c("khaki4", "blue", "green", "gold", "magenta",
                                 "red", "#0072B2", "#CC79A7", "#000000")) + xlab("") + 
                   ylab("sqrt eigenvalues") + ggtitle(paste0("n = ", num_samp[i], ", p = 100")) + 
                   theme_bw() + theme(legend.position="none")
}

grid.arrange(gg[[9]], gg[[10]], gg[[11]],
             gg[[12]], nrow = 2, ncol = 2)
```

```{r fig.height=8, fig.width=10}
grid.arrange(gg[[1]], gg[[2]], gg[[3]], gg[[4]],
             gg[[5]], gg[[6]], gg[[7]], gg[[8]],
             gg[[9]], gg[[10]], gg[[11]], gg[[12]],
             nrow = 4, ncol=3, as.table=FALSE)
```

